\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}		% Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}

\title{
	% An investigation into
	On the feasibility of leveraging upper storage zones
        of Japanese public dam reservoirs for hydro-power generation
}

%\date{September 9, 1985}	% Here you can change the date presented in the paper title
%\date{} 					% Or removing it

\author{ Tristan \\
	Kobe University\\
	\texttt{tristan@people.kobe-u.ac.jp} \\
	\And
	Yoshimi \\
	Kobe University\\
	\texttt{yoshimi@kobe} \\
	\And
	Rousslan \\
	Kobe University\\
	\texttt{rousslan@kobe} \\
	\And
	Victor \\
	CNES\\
	\texttt{victor@cnes} \\	
	\And
	Takiguchi \\
	Kobe University\\
	\texttt{Takiguchi@kobe} \\	
	\And
	Oishi \\
	RIKEN\\
	\texttt{oishi@riken} \\	
}

% Uncomment to remove the date
\date{}

% Uncomment to override  the `A preprint' in the header
%\renewcommand{\headeright}{Technical Report}
%\renewcommand{\undertitle}{Technical Report}
%\renewcommand{\shorttitle}{\textit{arXiv} Template}
\renewcommand{\shorttitle}{ }

%%% Add PDF metadata to help others organize their library
%%% Once the PDF is generated, you can check the metadata with
%%% $ pdfinfo template.pdf
\hypersetup{
pdftitle={A template for the arxiv style},
pdfsubject={q-bio.NC, q-bio.QM},
pdfauthor={David S.~Hippocampus, Elias D.~Striatum},
pdfkeywords={First keyword, Second keyword, More},
}

\begin{document}
\maketitle

\begin{abstract}

% Optimal dam management needs good forecast of futur income 
Dam operation is a problem of control under uncertainty,
as optimal policies are functions of 
noisy forecasts of river discharges incoming to dam reservoirs.
% Two main sources of uncertainty 
The uncertainty in discharge forecast can be attributed to two main factors:
Uncertainty in atmospheric (mostly precipitation) forecasts,
and in hydrological (mostly evaporation and runoff) modeling.
% Traditionally, the uncertainty has lead to conservative policies
High levels of uncertainty and abundant alternative sources of power generation
have lead Japanese public dam operators to adopt conservative operation strategies
so as to minimize the risk of dam failures.
However two factors may come to challenge this status quo:
% 1 As fire and atomic sources goes off, the value of low-carbon non-intermitent energy increases
%First, as social and environmental pressures threaten the long term viability of fossile fuel 
%and atomic plant receive increased criticism for social and environmental reasons.
First, social and environmental pressures on fossil fuel and nuclear energy production 
are foreseen to increase the value of hydrological power generation. 
% 2 As climate modeling and forecast technologies keep improving
Second, advances in both environmental modeling and statistical inference models
are foreseen to increase the accuracy of forecast.
Combined, these two factors may challenge the current risk-benefit analysis 
of dam operation towards adopting policies more focused on energy production.
This work aims to lay out the foundations for a large scale study 
on the feasibility of implementing such policies.
We do so by providing the following three contributions.
First we propose a conceptual framework to XXX.
Second, we propose a dataset to benchmark the accuracy 
of different atmospheric and hydrological models on this problem.
Finally we investigate the impact of
%We have open-sources all data and code, 
%and provide interactive tutorials for data scientists, hydrologist or climate specialist to easily join in on our effort.
%assembled a dataset, proposed a conceptual framework, 
%and analyze the accuracy  models.
%The goal is to quantify the impact of weather and hydrological 
%forecast accuracies on hydro-power generation of Japanese national dams. 
% Keyword: integrated approach.

\end{abstract}

% keywords can be removed

\keywords{Dam Reservoir Operation \and Hydro Power Generation \and Discharge Forecast \and Reinforcement Learning \and Machine Learning}

\section{Introduction}
\label{sec:Introduction}

%% Many mountains and a lot of rain=good for hydro power.
A mountainous topology and a heavy rain climate lend Japan a high potential for hydro power generation \cite{}. 
% Historical perspective
Historically\cite{}, Japan has extensively relied on its hydrological power generation up until the second world war.
As the period of great economic development called for increased energy consumption, 
fossil fuel plants have come to fill this demand for their ability to quickly and efficiently provide for this sudden jump in demand.
Later, the oil shock has seen Japan develop nuclear power generation for strategical reasons, to ensure its energy independency. 

% Current situation
%% Nuclear and fossil fuel contested
Nuclear incidents and international pledges to reduce carbon emissions have come to threaten the long term viability of the current energy mix.

%% Renewable energies are intermittent
As solar and wind power generation is being pushed forward, 
they are widely considered as inufficient in their own due to their intermittent nature. \cite{}

%% Variety of hydro provide low-carbon, non-itermittent, both base load and demand response.
Hydro is low-carbon and a variety of hydro power plant can bring both base load and demand response. 

%% For all its benefits, voices are calling for the optimization of Japanese dam operations.
For all its benefits, voices are calling for the optimization of Japanese dam operations. \cite{}
%% Probably more to say, what exactly?

% Fundamental problem:
The fundamental problem of dam operation is that of two opposing objectives\cite{}:
On the one hand energy production (as well as irrigation) 
benefits from keeping high levels of water into the reservoir. 
Indeed the higher water levels are, the more potential energy it stores, 
thus the more energy it can create for a given volume of output water discharge. 
On the other hand, flood control benefits from low level of reservoir filling,
as lower water levels enable to hold more incoming water, 
thus better buffering high discharge flows to prevent potential floods. 
An optimal operation policy is one that maximizes energy production while minimizing the risk of flooding.
However, keeping appropriate levels in the reservoir at each time requires knowledge 
of the amount of water flowing into the reservoir ahead of time, i.e. accurate river discharge forecast.

% In particular dam failures.
In particular, optimizing dam operation for energy production comes with a risk of dam failures:
Dam failure happens when the the dam reaches its full capacity due to large volume 
of water flowing into the reservoir.
In such cases, the reservoir is then brutally emptied to prevent the dam infrastructure to collapse 
under the forces exerced by the water, thus flooding the downstream areas, 
at great cost for the population living there. 

% Illustartion of impact of forecast accuracy.
Highly accurate river discharge forecast enable dam operators 
to keep reservoirs high to maximize energy production 
while ensuring dam failures do not occur.
In contrast, inaccurate river discharge forecast force dam operators 
to keep lower water levels in the reservoir to avoid dam failures in case of unexpected sudden inflows,
resulting in inefficient power generation policies.

% Nature of uncertainty
Two main factors are responsible for the uncertainty in river discharge forecast,
Atmospheric forecast, and hydrological modeling.

% Our analysis quantifies the impact of each factor independantly
% 
% Ok
% 
% Ok
%  

% Summary of contributions
Summary of contributions: 




\begin{itemize}
	\item Data operational
	\item Operational models for reservoir input flow
	\item Methodolody: Vertical integration.
	\item Open-source everything with easy-to-use tutorials for researchers to join.
\end{itemize}

% Notes on limitations
Limitations

\begin{itemize}
	\item No multi-purpose
	\item No multi-dam
\end{itemize}

% Positive note
Nevertheless, we hope it's useful, and can serve to build more onto.

\section{Related Work}
\label{sec:Related Work}

% Discharge computation
Hydro modeling

% Discharge forecast
Hydro forecast

% Dam operation
Dam operation.

% What else?
What else?

\section{Methodolody}
\label{sec:Methodolody}

\subsection{Overview}
\label{sec:Overview}

% What else
What else

\subsection{Meteorological model}
\label{sec:Meteorological model}

The meteorological model provides atmospheric variables.


\subsection{Hydrological Model}
\label{Hydrological Model}

The hydro model output river discharge incoming to the dam reservoir 
from the atmospheric variables, either observed or forecasted. 

\subsection{Dam Model}
\label{Dam Model}

Reservoir geometry: We infer the maximum volume from the observations. 
We infer the maximum height from Wikipedia. We then implemented both trapezoid and truncated cone geometry for the dam reservoir. 

Operation: We define two doors, one big door that does not produce energy. 
The dimension of the door is inferred from data (= to the max observed outflow release). 
One small door that produces electricity (heuristic size = 1/50th of the big door).


\subsection{Grid Response}
\label{Grid Response}

The grid response model defines the reward $r$ obtained for a given power production $P$ at a given time $t$.
This reward can be though of as a profit in a free-market economy, and is the sum of two terms:

$$ r = r_p(P, t) + r_n(t)$$

The positive reward quantifies the benefit of energy produced.
Currently, we use $r_p(P, t)=P$, considering constant value over time of the generated power.
However, hydro's value lies in its non-intermittence to supplement intermittent sources.
Integrating the fluctuations of intermitent sources and their impact on the value of hydro power generation 
at different seasons and time of the day may prove interesting for future research.

The negative reward quantifies the cost of a dam failure.
We set this cost to be constant $r_n(t)=C$ per dam,
as the maximum positive reward that can be produced by this dam over the whole period of operation,
so that the negative impact of a single dam failure over the whole period of activity 
would outweight the benefits of full power production of the whole dam operation.

\subsection{Dam Operation Model}
\label{sec: Dam Operation Model}

Every hour, the dam operator can either open the big door, the small door or do nothing for one hour: 
Action space $ \mathcal{A} = \{a1, a2, a3 \}$

Decisions are made based on the current level of the reservoir as well as the future input discharge forecast for a given horizon.
State space S = [Current volume / height, inflow forecasts]

Our goal is to learn a policy function $\Pi: \mathcal{S} \rightarrow \mathcal{A}$ that maximizes reward.
The reward for electricity production is proportional to the height of the water level times the volume of water discharged. Negative reward is also associated with dam failures:


\section{Proposed Dataset}
\label{sec:Proposed Dataset}


\section{Optimal Dam Operation}
\label{sec:Hydrological Uncertainty}

We start by optimizing the dam without any uncertainty.

\subsection{Baseline}
\label{sec:Dam Operation baseline}

\subsection{Optimal Operator}
\label{sec:Optimal Operator}

\subsection{Operation Under Uncertainty}
\label{sec:Operation Under Uncertainty}

\subsection{Experiment}
\label{sec:Hydrological Uncertainty}

 - Answers the following question:

1. What is the forecast horizon needed in order to keep the dam from overflowing?
-> Show as input distribution.

2. Impact of state design on RL baseline.

3. Show the ideal model is brittle. How?

\section{Hydrological Uncertainty}
\label{sec:Hydrological Uncertainty}

In this section, we use assimilated data, no forecast.

\subsection{Hydrological Models}
\label{sec:Hydrological Models}

Use Camaflood, conceptual rainfall runoff, linear, non-linear and deep machine learning models.

\subsection{Experiments}
\label{sec:Hydrological Experiments}

\subsubsection{Discharge prediction}

Show accuracy of different models.

\subsubsection{Dam operation}

Show reward of different models.

\begin{table}
	\caption{Model accuracy}
	\centering
	\begin{tabular}{lll}
		\toprule
		\multicolumn{2}{c}{Part}                   \\
		\cmidrule(r){1-2}
		Name     & Description     & Size ($\mu$m) \\
		\midrule
		Dendrite & Input terminal  & $\sim$100     \\
		Axon     & Output terminal & $\sim$10      \\
		Soma     & Cell body       & up to $10^6$  \\
		\bottomrule
	\end{tabular}
	\label{tab:table}
\end{table}

\section{Meteorological Uncertainty}
\label{sec:Meteorological Uncertainty}

\subsection{Meteo Data}
\label{sec:Meteo Data}

\subsection{Experiments}
\label{sec:Meteo Experiments}

Use different data source.


\subsection{Meteorological Uncertainty}

\section{Limitations}

\begin{itemize}
	\item No multi-purpose
	\item No multi-dam
 	\item No explicit evaporation modeling
	\item Heuristic dimensioning.
	\item No river and snow gauge.  
\end{itemize}

\section{Conclusion}
\label{sec:Conclusion}

Conclusion

\bibliographystyle{unsrtnat}
\bibliography{references}  %%% Uncomment this line and comment out the ``thebibliography'' section below to use the external .bib file (using bibtex) .


%%% Uncomment this section and comment out the \bibliography{references} line above to use inline references.
% \begin{thebibliography}{1}

% 	\bibitem{kour2014real}
% 	George Kour and Raid Saabne.
% 	\newblock Real-time segmentation of on-line handwritten arabic script.
% 	\newblock In {\em Frontiers in Handwriting Recognition (ICFHR), 2014 14th
% 			International Conference on}, pages 417--422. IEEE, 2014.

% 	\bibitem{kour2014fast}
% 	George Kour and Raid Saabne.
% 	\newblock Fast classification of handwritten on-line arabic characters.
% 	\newblock In {\em Soft Computing and Pattern Recognition (SoCPaR), 2014 6th
% 			International Conference of}, pages 312--318. IEEE, 2014.

% 	\bibitem{hadash2018estimate}
% 	Guy Hadash, Einat Kermany, Boaz Carmeli, Ofer Lavi, George Kour, and Alon
% 	Jacovi.
% 	\newblock Estimate and replace: A novel approach to integrating deep neural
% 	networks with existing applications.
% 	\newblock {\em arXiv preprint arXiv:1804.09028}, 2018.

% \end{thebibliography}


\end{document}
